Placeholder

### 2021-03-16 Paper_Histograms.Rmd
Added '2' above the retro gender plot for the link to the second figure caption

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())  +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

>>>>

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())  +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
  geom_text(x = Inf, y = Inf, label = "2", hjust = 1, vjust = 1)
